Sketch of DP - Bayesian Inference

### 2018-07-17 main-sketch.tex
section 4 pass

\section{The Problem and Baseline approach}
We are interested in designing a mechanism for privately releasing
\emph{fully} the posterior distributions derived in section \ref{sec_background},
and not a sample from them.  It's worth noticing that the posterior
distributions are fully characterized by their parameters, and the
family (beta, Dirichlet) they belong to.  Hence, in case of the
Beta-Binomial model we are interested in releasing a private version
of the pair of parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
in the case of the Dirichlet-Multinomial model we are interested in a
private version of $\valpha'=(\valpha + \Delta \valpha)$. \citet{zhang2016differential} and \citet{xiao2012bayesian} have
already attacked this problem and their solution consisted in adding
independent Laplacian noise to the parameters of the posteriors. That
is, in the case of the Beta-Binomial system the value released would
be: $(\tilde\alpha,\tilde\beta)=(\alpha + \Delta \tilde\alpha,\beta + n - \Delta \tilde\alpha)$ where $\Delta \tilde\alpha\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$, and
%with truncating method come from algorithm designed by \citet{zhang2016differential}
where $Lap(\mu,\nu)$
denotes a Laplacian random variable with mean $\mu$ and scale $\nu$.
This mechanism is $\epsilon$-differentially private, and the noise is
calibrated w.r.t to a sensitivity of 2 which is derived by using
$\ell_1$ norm over the pair of parameters. Indeed, considering two
adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } data observations
$\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
distributions, characterized by the pairs
$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
This argument extends similarly to the Dirichelet-Multinomial system.

@@

\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)})}
{\displaystyle\sum_{r\in\betaset} exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)})}
\end{equation*}
this mechanism is based on the basic exponential mechanism \cite{talwar}, with $\betaset$ as range and $\hellinger(\cdot,\cdot)$ as scoring function.
The difference is that in this mechanism we don't calibrate the noise w.r.t to the global sensitivity of the scoring function but w.r.t to the smooth sensitivity $S(\dataobs)$
-- \citet{nissim2007smooth}-- of $\hellinger(\bysinfer(\dataobs), \cdot)$. The smooth sensitivity is computed as follows:
\begin{equation}
  \label{eq:smooth}
   S(\dataobs)=\max_{\dataobs' \neq \dataobs, \dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )\cdot e^{-\gamma\cdot d(\dataobs, \dataobs')}\bigg\}
\end{equation}
 where $d$ is the Hamming distance between two datasets,  $\gamma = \gamma(\epsilon, \delta)$ is a function
 of $\epsilon$ and $\delta$ to be determined later, and where $\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$
 denotes the local sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$ --w.r.t $\ell_1$ norm--of the scoring function used in our mechanism, that is:
 \begin{equation*}
 \Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )=\max_{\dataobs'' \in \datauni^n:\adj{\dataobs'}{\dataobs''}, r\in \betaset}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs''), r)\rvert
\end{equation*}

@@

\begin{theorem}[Privacy] 
  For  $\gamma=\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, then both
  $\hexpmech$ and $\hexpmechd$ are $(\epsilon,\delta)$-differentially private.
\end{theorem}

@@

\section{Preliminary Experimental Results}
\label{sec_experiment}

\subsection{Accuracy Trade-off Evaluation wrt. Different Variables}
\label{subsec_vs_variables}

In this section, we evaluate the accuracy wrt. four variables, including data size, dimension, data variance and prior distribution, and some combinations of these variables. We experiment 1000 times under each value of variables and produce 4-quantile plots for each variable. In following 4-quantile plots, the y-axis is accuracy measured by Hellinger distance, x-axis is different value of variables. The blue boxes in plots represent our exponential mechanism and the next yellow box represents the Laplace mechanism under the same setting.

\subsubsection{Accuracy Evaluation wrt. Datasize}
\label{subsubsec_vs_datasize}

@@

In Fig. \ref{fig_vs_datasize}, both of the two plots show that when data size go larger, accuracy of our exponential mechanism are decreasing. In Fig. \ref{fig_vs_datasize}(a), when the data size is smaller than 12, we can beta Laplace mechanism but fail when data size larger than or equal to 12. Same as in Fig. \ref{fig_vs_datasize}(b), we can beat Laplace mechanism when data size is smaller than 15 and fail otherwise.

>>>>

\section{The Problem and Baseline approach}
\label{sec:base}
We are interested in designing a mechanism for privately releasing
\emph{fully} the posterior distributions derived in section \ref{sec_background},
and not a sample from them.  It's worth noticing that the posterior
distributions are fully characterized by their parameters, and the
family (beta, Dirichlet) they belong to.  Hence, in case of the
Beta-Binomial model we are interested in releasing a private version
of the pair of parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
in the case of the Dirichlet-Multinomial model we are interested in a
private version of $\valpha'=(\valpha + \Delta \valpha)$. \citet{zhang2016differential} and \citet{xiao2012bayesian} have
already attacked this problem and their solution consisted in adding
independent Laplacian noise to the parameters of the posteriors. That
is, in the case of the Beta-Binomial system the value released would
be: $(\tilde\alpha,\tilde\beta)=(\alpha + \Delta \tilde\alpha,\beta + n - \Delta \tilde\alpha)$ where $\Delta \tilde\alpha\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$, and
%with truncating method come from algorithm designed by \citet{zhang2016differential}
where $Lap(\mu,\nu)$
denotes a Laplacian random variable with mean $\mu$ and scale $\nu$.
This mechanism is $\epsilon$-differentially private, and the noise is
calibrated w.r.t. to a sensitivity of 2 which is derived by using
$\ell_1$ norm over the pair of parameters. Indeed, considering two
adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } data observations
$\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
distributions, characterized by the pairs
$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
This argument extends similarly to the Dirichelet-Multinomial system.

@@

\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)})}
{\displaystyle\sum_{r\in\betaset} exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)})}
\end{equation*}
this mechanism is based on the basic exponential mechanism \cite{talwar}, with $\betaset$ as range and $\hellinger(\cdot,\cdot)$ as scoring function.
The difference is that in this mechanism we don't calibrate the noise w.r.t. to the global sensitivity of the scoring function but w.r.t. to the smooth sensitivity $S(\dataobs)$
-- \citet{nissim2007smooth}-- of $\hellinger(\bysinfer(\dataobs), \cdot)$. The smooth sensitivity is computed as follows:
\begin{equation}
  \label{eq:smooth}
   S(\dataobs)=\max_{\dataobs' \neq \dataobs, \dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )\cdot e^{-\gamma\cdot d(\dataobs, \dataobs')}\bigg\}
\end{equation}
 where $d$ is the Hamming distance between two datasets,  $\gamma = \gamma(\epsilon, \delta)$ is a function
 of $\epsilon$ and $\delta$ to be determined later, and where $\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$
 denotes the local sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$ --w.r.t. $\ell_1$ norm--of the scoring function used in our mechanism, that is:
 \begin{equation*}
 \Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )=\max_{\dataobs'' \in \datauni^n:\adj{\dataobs'}{\dataobs''}, r\in \betaset}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs''), r)\rvert
\end{equation*}

@@

\begin{theorem}[Privacy] 
  For  $\gamma=\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, both
  $\hexpmech$ and $\hexpmechd$ are $(\epsilon,\delta)$-differentially private.
\end{theorem}

@@

\section{Preliminary Experimental Results}
\label{sec_experiment}
In this section, we evaluate the accuracy of the mechanisms defined in
Section (\ref{sec_smoo}) w.r.t. four variables, including data size, dimensions,
data variance, prior distribution, and some combinations thereof.
Every plot is an average over 1000 runs.

\noindent In the following whiskers-plots, the y-axis shows the accuracy (or equivalently, the error) of the mechanisms.
Accuracy is measured using Hellinger distance. The x-axis, instead shows  one of the previously mentioned
independent variables --or a combination thereof.
The boxes extend from the lower to the upper quartile values of the data, with a line at the median. A notch on the box around the median
is also drawn to give a rough guide to the significance of difference of medians;
The whiskers extend from the box to show the range of the data. 
A blue box in the plots represents the exponential mechanism behaviour,
while the yellow box next to it represents the performance of a variation of the
basic Laplace mechanism presented in Section (\ref{sec:base}) with the same settings: that is $\epsilon, \delta$, data, prior.
The variation considered performs a post processing on the released parameters so that they
are consistent. For instance in the case \todo{more info about the truncation}.
\subsubsection{Evaluation w.r.t. Datasize}
\label{subsubsec_vs_datasize}

@@

In Fig. \ref{fig_vs_datasize} we consider \emph{balanced} datasets of observations.
This means that in the Beta-Binomial setting the datasets will be
half 1s and half 0s, while int the Dirichelet-Multinomial the data will be
equally split in all the $k=3$ bins. Fig. \ref{fig_vs_datasize} shows that  when the
data size increases, the accuracy of $\hexpemech$ and $\expmechd$
decreases. In Fig. \ref{fig_vs_datasize}(a), when the data size is
smaller than 12, $\hexpmech$ outperforms the Laplace mechanism but fails to do so
for bigger datasets. The same happens in as in Fig. \ref{fig_vs_datasize}(b),
we can beat Laplace mechanism when data size is smaller than 15 and
fail otherwise.
